I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-10-12 paper_io_sim.tex
Figure explanation

\author{\IEEEauthorblockN{Hoang-Dung Do, Tristan Glatard, Val\'erie Hayot-Sasson
  }\\
  \IEEEauthorblockA{
    Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada
  }
}

@@

			\subsubsection{Evaluation on storage types}

		    Since different storage types should also be taken into account, 
		    we conduct another experiment with the same scenario as 
		    in the multi-threaded experiment, except that files are stored on a 
		    shared file system instead of local disk.

		    \textcolor{red}{[Description of Lustre on the cluster and how it's 
		    simulated]}.

@@

			Again, with 100GB input file, memory behavior in the third read in the 
			simulators is different from reality, causing unexpected long read time, 
			which we have seen in Figure~\ref{fig:single_error_100}. 
			This can be explained with the amount of cached data of files at the beginning 
			of the read shown in Figure~\ref{fig:fincore}. 
			In real pipeline execution, after \textit{write2}, which writes \textit{file3}, 
			all data of \textit{file3} is in cache (Figure~\ref{fig:fincore_real}). 
			Thus, in \textit{read3}, \textit{file3} is read with memory bandwidth. 
			But in our simulator, after \textit{write2}, only a part of \textit{file3} 
			remains in cache (Figure~\ref{fig:fincore_wrench}). 
			The reason is while \textit{file3}  is being written, the page cache is saturated, 
			and eviction is evoked to evict data from page cache, make space 
			available for \textit{file3} data. 
			However, because the amount of evictable memory is less than required amount, 
			some \textit{file3} data is evicted after being written, make \textit{file3} 
			partially cached. As a result, in \textit{read3}, only a part of \textit{file3} is read 
			from cache with memory bandwidth, a part of it is read from disk with disk read 
			bandwidth, which is many times slower, leading to longer read time.

>>>>

\author{\IEEEauthorblockN{Hoang-Dung Do, Val\'erie Hayot-Sasson, Tristan Glatard
  }\\
  \IEEEauthorblockA{
    Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada
  }
}

@@

			\subsubsection{Evaluation on remote storage}

		    Since remote storage is common in HPC, we conduct another experiment with 
		    the same scenario as in the multi-threaded experiment, except that files 
		    are stored on a node and read by another node.

@@

			Again, with 100GB input file, memory behavior in the third read in the 
			simulators is different from reality, causing unexpected long read time, 
			which we have seen in Figure~\ref{fig:single_error_100}. 
			This can be explained with the amount of cached data of files at the beginning 
			of the read shown in Figure~\ref{fig:fincore}. 
			In this figure, \textit{file\_i} is the input of \textit{read\_i} and output of \textit{write\_i-1}. 
			In real pipeline execution, after \textit{write2}, which writes \textit{file3}, 
			all data of \textit{file3} is in cache (Figure~\ref{fig:fincore_real}). 
			Thus, in \textit{read3}, \textit{file3} is read with memory bandwidth. 
			But in our simulator, after \textit{write2}, only a part of \textit{file3} 
			remains in cache (Figure~\ref{fig:fincore_wrench}). 
			The reason is while \textit{file3}  is being written, the page cache is saturated, 
			and eviction is evoked to evict data from page cache, make space 
			available for \textit{file3} data. 
			However, because the amount of evictable memory is less than required amount, 
			some \textit{file3} data is evicted after being written, make \textit{file3} 
			partially cached. As a result, in \textit{read3}, only a part of \textit{file3} is read 
			from cache with memory bandwidth, a part of it is read from disk with disk read 
			bandwidth, which is many times slower, leading to longer read time.
